\documentclass[11pt]{article}

\usepackage{url}
\usepackage{array}
\usepackage{multicol}
\usepackage{tabu}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usepackage{fancyhdr}
\usepackage[margin=.7in]{geometry}
\usepackage[hang,flushmargin,symbol*]{footmisc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}
\definecolor{darkblue}{rgb}{0, 0, .6}
\definecolor{grey}{rgb}{.7, .7, .7}
\usepackage[breaklinks]{hyperref}

\theoremstyle{definition} 
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{important}[theorem]{Important Note}
\newtheorem{recall}[theorem]{Recall}
\newtheorem{note}[theorem]{Note}
\newtheorem{question}[theorem]{Question}
\newtheorem*{definition*}{Definition}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{claim*}{Claim}

\newcommand{\ds}{\displaystyle}
\newcommand{\Spin}{\operatorname{Spin}}
\newcommand{\Rng}{\operatorname{Rng}}

\setlength{\parindent}{0pt}
\setlength{\fboxsep}{10pt}

%%%%%%Header/Footer%%%%%%%

\pagestyle{fancy}

\lhead{\scriptsize  MAT 511: Abstract Algebra I - Fall 2021} 
\chead{} 
\rhead{\scriptsize Exam 1} 
\lfoot{\scriptsize This work is licensed under the \href{https://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons Attribution-Share Alike 4.0 License}.} 
\cfoot{} 
\rfoot{\scriptsize Written by \href{http://dcernst.github.io}{D.C. Ernst}} 
\renewcommand{\headrulewidth}{0.4pt} 
\renewcommand{\footrulewidth}{0.4pt}

%%%%%%%%%%%%%%%%%%%

\begin{document}

\tikzstyle{vert} = [circle, draw, fill=grey,inner sep=0pt, minimum size=6mm]
\tikzstyle{vertsmall} = [circle=3pt, draw, fill=grey]
\tikzstyle{s} = [draw, very  thick, black, stealth-stealth]
\tikzstyle{s1} = [draw, very  thick, black,-stealth]
\tikzstyle{d} = [draw, very  thick, black, dashed,-stealth]
\tikzstyle{d2} = [draw, very thick, dashed,stealth-stealth]
\tikzstyle{s2} = [draw, very thick, stealth-stealth]
\tikzstyle{snake} = [draw, very thick, snake it,-stealth]
\tikzstyle{snake2} = [draw, very thick, snake it, stealth-stealth]
\tikzstyle{g} = [draw, very thick, grey,-stealth]
\tikzstyle{g2} = [draw, very thick, grey, stealth-stealth]

\begin{center}

{\Large\bf Exam 1}

\bigskip

  \fbox{\parbox{7in}{
    \vspace{5pt}
    \textbf{\large Your Name:}
    \vspace{5pt}
  }}
  
  \bigskip
  
  \fbox{\parbox{7in}{
    \vspace{5pt}
    \textbf{\large Names of Any Collaborators:}
    \vspace{5pt}
  }}

\end{center}

\section*{Instructions}

Answer each of the following questions by \textbf{11:59\textsc{pm} on Tuesday, October 5}. If you cannot submit a physical copy of the exam, email me a PDF to confirm that you finished your exam on time and then give me a physical copy the next time you see me. This exam is worth a total of 29 points and is worth 20\% of your overall grade.

\bigskip

I expect your solutions to be \emph{well-written, neat, and organized}.  Do not turn in rough drafts.  What you turn in should be the ``polished'' version of potentially several drafts.  Feel free to type up your final version.  The \LaTeX\ source file of this exam is also available if you are interested in typing up your solutions using \LaTeX.  I'll gladly help you do this if you'd like.

\bigskip

Reviewing material from previous courses and looking up definitions and theorems you may have forgotten is fair game. However, when it comes to completing the following problems, you should \emph{not} look to resources outside the context of this course for help.  That is, you should not be consulting the web, other texts, other faculty, or students outside of our course in an attempt to find solutions to the problems you are assigned.  This includes Chegg and Course Hero. On the other hand, you may use each other, the textbook, me, and your own intuition. Further information:
\begin{enumerate}
\item You may freely use any theorems that we have discussed in class, but you should make it clear where you are using a previous result and which result you are using.  For example, if a sentence in your proof follows from Problem X.Y, then you should say so.
\item Unless you prove them, you cannot use any results from the course notes that we have not yet covered.
\item You are \textbf{NOT} allowed to consult external sources when working on the exam.  This includes people outside of the class, other textbooks, and online resources.
\item You are \textbf{NOT} allowed to copy someone else's work.
\item You are \textbf{NOT} allowed to let someone else copy your work.
\item You are allowed to discuss the problems with each other and critique each other's work.
\end{enumerate}

\begin{center}
\textbf{I will vigorously pursue anyone suspected of breaking these rules.}
\end{center}

You should \textbf{turn in this cover page} and all of the work that you have decided to submit. \textbf{Please write your solutions and proofs on your own paper.} To convince me that you have read and understand the instructions, sign in the box below.

\bigskip

  \fbox{\parbox{7in}{
    \vspace{5pt}
    \textbf{\large Signature:} \hfill
    \vspace{5pt}
  }}

\bigskip

Good luck and have fun!

\newpage

For the following problems you will need to digest new content in our problem sequence.  We will spend time discussing some of these concepts in class during the time you have available to work on the exam. However, you should not wait until I have discussed the relevant topics.  Just dig in and get started.

\bigskip

For each problem you may only use results from the book that come before the corresponding problem. 

\begin{enumerate}

\item Complete \textbf{all} of the following.
\begin{enumerate}
\item (3 points) Problem 1.123
\item (2 points) Problem 1.124
\item (2 points) Problem 1.125. \emph{Note:} This problem is similar to Problem~1.42, but you cannot simply cite that problem.
\item (2 points) Problem 1.126
\end{enumerate}

\item (4 points each) Complete \textbf{two} of the following.
\begin{enumerate}
\item Problem 1.134. \emph{Note:} This problem together with our definition of order of an element immediately implies Problem~1.135, which provides a useful characterization of order of an element.
\item Problem 1.139. \emph{Note:} Since $g^0=e$, Problem~1.139 immediately implies Problem~1.140.
\item Problem 1.143
\item Problem 1.144
\end{enumerate}

\item (4 points) Prove Problem~1.141.

\item (4 points each) Complete \textbf{two} of the following.
\begin{enumerate}
\item Problem 2.19
\item Problem 2.23(a)
\item Problem 2.23(b)
\item Problem 2.24
\item Problem 2.31
\end{enumerate}

\end{enumerate}

\end{document}